\subsection{Operator:} Unitary procedure for transforming information or implement the behavior of the algrithm.

\subsection{Solution:} Array of $n$ columns containing a solution for a given problem. In the binary case, the posible values are $0$ and $1$.

\subsection{Constrain:} Conditions to be met to find a viable solution.

\subsection{Benchmark:} Optimal set of known problem instances to validate the propose algorithm.

\subsection{Objective Function:}  Implements the mathematical expression representing the problem to solve.

\subsection{Fitness:} Value resulting by applying the objective function to solution.

\subsection{Matrix of Costs:} Consist of $n$ columns vector containing the cost associated with each problem variable.

\subsection{Optimal Value:} Solution with the best fitness.

\subsection{Domain:} Set of possible values for the variable.

\subsection{Matrix A:} Matrix containing the restrictions for the given problem.

\subsection{RPD:} Relative Percentage Deviation.

\subsection{Harmony Memory:} Memory space which includes the population of the solution vectors.

\subsection{Harmony Memory Size:} Defines the amount of harmonies that can be stored in HM.

\subsection{Harmony Memory Consideration Rate (HMCR):} In memory consideration, the value of decision variable ${x\textprime}_1$ is randomly selected from the historical values, other decision variables, $({x\textprime}_2, {x\textprime}_3,\dots,{x\textprime}_N)$ are sequentially selected in the same manner with probability where HMCR $\in$ (0,1).

\subsection{Pitch Adjusting Rate (PAR):} Each decision variable ${x\textprime}_i$ assigned a value by memory considerations is pitch adjusted with the probability of PAR where PAR $\in$ (0,1).



